---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# testpackage

<!-- badges: start -->
<!-- badges: end -->

The goal of testpackage is to provide some helper functions for people working with HSRC or other projects.  

There are currently two independent tools.

`pretty_plot` adds a logo and some text (e.g. source, date etc) to a plot.
`QR_save` generates a series of QR codes from a csv file of URLs and titles. Useful for presentations.

## Installation

You can install the development version of testpackage from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("IainMoppett/testpackage")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(testpackage)
## basic example code

QR_save(system.file("extdata", "QR_Data.csv", package = "testpackage"))
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
library(testpackage)

QR_save(system.file("extdata", "QR_Data.csv", package = "testpackage"))

plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
