---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# testpackage

<!-- badges: start -->
<!-- badges: end -->

The goal of testpackage is to provide some helper functions for people working with HSRC or other projects.  

There are currently three independent tools.

`pretty_plot` adds a logo and some text (e.g. source, date etc) to a plot.
`theme_HSRC` creates a ggplot theme 
`QR_save` generates a series of QR codes from a csv file of URLs and titles. Useful for presentations.

## Installation

You can install the development version of testpackage from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("IainMoppett/testpackage")
```

## Example

### QR_save

Use the `QR_save` function to save a series of pdfs of QR codes with a helpful title. Online tools tend to give a rather unhelpful 'file.png' as the output.

```{r example}
library(testpackage)
## basic example code

QR_save(system.file("extdata", "QR_Data.csv", package = "testpackage"))
```

### Pretty_plot

Adds a logo at the bottom right and some text (e.g. data source) at the bottom left. Plots can be set-up using
whatever themes you choose. Or you can override the theme with `theme_HSRC` by setting `theme_apply` to `TRUE.`  

Two native test plots

```{r test_plots, echo = FALSE}
library(testpackage)
library(ggplot2)

pl_1 <- ggplot(mpg, aes(displ, hwy, colour = class)) + geom_point()
pl_1_no_legend <- ggplot(mpg, aes(displ, hwy, colour = class)) +
geom_point(show.legend = FALSE)

pl_1
pl_1_no_legend

```

Pretty_plot function applied to the test plots
```{r pretty_plots, echo = FALSE}
pp_pl_1 <- pretty_plot(pl_1, source = "Text 14 point, native theme",
logo_path = system.file("extdata", "SNAP3_2019.jpg", package = "testpackage"),
text_size = 14,
theme_apply = FALSE)

pp_pl_1

pp_pl_1_no_legend <- pretty_plot(pl_1, source = "Text 16 point, HSRC theme",
logo_path = system.file("extdata", "SNAP3_2019.jpg", package = "testpackage"),
text_size = 16,
theme_apply = TRUE)
pp_pl_1_no_legend
```

